The Eclipse Integrated Computational Environment

### 2019-06-23 src/content.tex
Modified content to fit thesis format.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{src/images/ICE-arch-1.jpg}
\caption{High-level architecture of ICE showing the relationships and rough division of responsibility between the five primary components of ICE. The ICE Core is responsible for the workflow management and delegations instructions and data to the Item and Data Structures, respectively. User input is received from the client or through headless interactions, while persistence of large amounts of data is delegated to a persistence service.}
\label{highlevel-arch}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{src/images/ICE-arch-2.jpg}
\caption{The architecture of the ICE Core and its dependencies. The ICE Core class handles communications between workflow Items and common data structures, but delegates construction of workflow Items to builders.}
\label{core-arch}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{src/images/ICE-arch-3.jpg}
\caption{The class hierarchy of ICE Items showing the relationships between the Item, its subclasses, and services that it uses. Vibe Launcher and MOOSE Launcher are examples of special Job Launch Items for executing jobs, and their applications are discussed in section \ref{illustrative-examples}.}
\label{item-arch}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{src/images/ICE-arch-4.jpg}
\caption{Common data structures and their relationships in ICE.}
\label{data-arch}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{images/vibe_20151016.png}
\caption{ICE workbench for VIBE analysis.}
\label{vibe}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{images/ice-moose.png}
\caption{ICE workbench for MOOSE workflows.}
\label{moose}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{images/ice-bjm.png}
\caption{ICE workbench for binder jet modeling.}
\label{binder}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{images/reflectivity-screenshot.png}
\caption{ICE workbench for neutron reflectivity.}
\label{reflectivity}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{images/jaded.png}
\caption{ICE workbench in the Jade Adiabatic Development Environment (JADE) for quantum computing simulations.}
\label{jade}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-1.jpg}
\caption{High-level architecture of ICE showing the relationships and rough division of responsibility between the five primary components of ICE. The ICE Core is responsible for the workflow management and delegations instructions and data to the Item and Data Structures, respectively. User input is received from the client or through headless interactions, while persistence of large amounts of data is delegated to a persistence service.}
\label{highlevel-arch}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-2.jpg}
\caption{The architecture of the ICE Core and its dependencies. The ICE Core class handles communications between workflow Items and common data structures, but delegates construction of workflow Items to builders.}
\label{core-arch}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-3.jpg}
\caption{The class hierarchy of ICE Items showing the relationships between the Item, its subclasses, and services that it uses. Vibe Launcher and MOOSE Launcher are examples of special Job Launch Items for executing jobs, and their applications are discussed in section \ref{illustrative-examples}.}
\label{item-arch}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ICE-arch-4.jpg}
\caption{Common data structures and their relationships in ICE.}
\label{data-arch}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/vibe_20151016.png}
\caption{ICE workbench for VIBE analysis.}
\label{vibe}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ice-moose.png}
\caption{ICE workbench for MOOSE workflows.}
\label{moose}
\end{figure}

@@

\begin{figure}[H]
\centering
\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/ice-bjm.png}
\caption{ICE workbench for binder jet modeling.}
\label{binder}
\end{figure}

@@

\begin{figure}[H]
\centering
\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/reflectivity-screenshot.png}
\caption{ICE workbench for neutron reflectivity.}
\label{reflectivity}
\end{figure}

@@

\begin{figure}[H]
\centering
\baseIncludegraphics{pubs/ice-softwarex-2017/src/images/jaded.png}
\caption{ICE workbench in the Jade Adiabatic Development Environment (JADE) for quantum computing simulations.}
\label{jade}
\end{figure}
